%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Niranjan Nagaraju
\documentclass[a4paper,margin,line]{resume}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Niranjan Nagaraju}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    No.\ 83, H.\ Colony,		                      	\hfill									   \vspace{0mm}\\\vspace{0mm}% 
    2nd Cross, Indiranagar,                       	\hfill mobile: +91 9900400100			   \vspace{0mm}\\\vspace{0mm}%
    Bangalore - 560038								\hfill e-mail: niranjan.nagaraju@gmail.com \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Career Interests
    \section{\mysidestyle Career\\Interests}

    Algorithms Design and Optimization  \vspace{1mm}\\%
	TCP/IP Networking \vspace{1mm}\\%
	Cryptography - Algorithms and applications to network security


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Visvesvaraya Technological University}, PES Institute of Technology, Bangalore \vspace{1mm}\\%
    \textsl{Bachelor of Engineering}, Computer Science \hfill \textbf{2002 -- 2006} \vspace{1mm}\\%
	Aggregate: 73.3 \% \hfill \vspace{0mm}\\\vspace{-4.5mm}%


	%__________________________________________________________________________________________________________________
    % Technical Skills
	\section{\mysidestyle Technical\\Skills} 
	
	Programming Languages: C, C++, Python, Haskell, Linux Shell scripting (Bash) \vspace{2mm}\\%
	Tools: Oprofile, Valgrind, W3af, GDB, Vim, Emacs \vspace{2mm}\\%
	Operating Systems: Windows, Linux, Mac OS X \vspace*{2mm}\\%
	Github:  \href{https://github.com/niranjan-nagaraju/}{\textbf{Link to Github Profile}}


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    
    \textbf{5.6} years of design and development experience in System Programming, Security,\\ 
	Device driver development and TCP/IP Networking.

    \href{http://www.rsa.com/}{\textbf{RSA Security}}, Bangalore \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{October 2010 -- Present}%

	\textsl{RSA Access Manager (AxM) Web Agents}
	\begin{itemize}
		\item Implemented features for Intersite Single Sign On (ISSO), Securing against arbitrary URL redirects (trusted domains).%
		\item Security audit of AxM Web agents using w3af/webscarab, Fortify and fixed critical security issues. %		
		\item Worked on the development of extending AxM Web Agents to support Email-based RSA Adaptive Authentication. %		
		\item Responsible for fixing high-priority customer issues. \vspace{0mm}\\\vspace{1mm}%
	\end{itemize}}


    \href{http://www.narus.com/}{\textbf{Narus Networks}}, Bangalore \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{June 2008 -- March 2010}%
	
	\textsl{Multi-threading processing layer}
	\begin{itemize}
		\item Worked on the development of an actor-based concurrent programming language to introduce multi-threaded efficiency in the processing layer.%
		\item Implemented Input/Output modules to be used in the new language dialects.%
		\item Profiling and performance tuning (Oprofile and Valgrind) %
	\end{itemize}

	\textsl{SQL Loader}
	\begin{itemize}
		\item Developed a Narus component to load capture layer metadata into an SQL database using unixODBC library. %
	\end{itemize}

	\textsl{Packet Loader}
	\begin{itemize}
		\item Developed a Narus component to analyze capture layer events/data based on user-configured targets and write the matching packets to PCAP and ETSI compliant Metadata files. \vspace{0mm}\\\vspace{1mm}%
	\end{itemize} 

    \href{http://www.coreel.com/}{\textbf{CoreEl Technologies}}, Bangalore \vspace{2mm}\\\vspace{1mm}%
    \textsl{Design Engineer} \hfill \textbf{July 2006 -- June 2008}%
	
	\textsl{TOE (TCP/IPv4 Offload Engine)}
	\begin{itemize}
		\item Developed a network device driver interface to load the PCI-e based hardware stack. %
		\item Design and implementation of a dual stack architecture for the TOE stack to coexist with the Linux TCP/IP stack. %
		\item Implemented ICMP echo (Ping) and ARP handling modules in software. %
	\end{itemize}
 
	\textsl{TIP6E (TCP/IPv6 Offload Engine)}
	\begin{itemize}
		\item Designed and implemented ICMPv6 NDP (Neighbor Discovery Protocol) and MLD (Multicast Listener Discovery) in software to be integrated with the rest of the IPv6 stack in the TIP6E hardware FPGA. %
	\end{itemize}

	\textsl{RPR (Resilient Packet Ring)}
	\begin{itemize}
		\item Implemented IOCTL interfaces for configuring the RPR stack in hardware. (RPR is a dual-ring based MAN (Metropolitan Area Network) technology). %
	\end{itemize}


%______________________________________________________________________________________________________________________
\section{\mysidestyle Corporate\\Training}

\href{http://www.sandeepani-vlsi.com/}{\textbf{Sandeepani School of VLSI Design}}, Bangalore \hfill \textbf{December 2006 -- March 2007}\\%
Taught C fundamentals and Data structures courses at Sandeepani, a corporate training division of CoreEl Technologies. 


%______________________________________________________________________________________________________________________
\section{\mysidestyle Internships} 

\textbf{Hewlett Packard}, Bangalore \vspace{2mm}\\\vspace{1mm}%
    \textsl{Gelato Vanilla Project/Apache} \hfill \textbf{February 2008 -- April 2008}\\%
Benchmarking and profiling the performance of Apache server on Linux/Itanium.


%______________________________________________________________________________________________________________________
\section{\mysidestyle Academic\\Projects}

S.M.A.R.T. Downloader
\begin{itemize}
	\item A download Manager written in C\#.net with zip preview, media preview, FTP support, auto-resume and concurrent multi-part download capabilities
\end{itemize}

Illuminati
\begin{itemize}
	\item An MS Paint like graphics editor program written in C/GTK+ on Linux.
\end{itemize}


%______________________________________________________________________________________________________________________
\section{\mysidestyle References} 

Available upon request


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

